Prefix-free graphs and suffix array construction in sublinear space

### 2023-06-20 manuscript/main.tex
added minted to results

%% Options:
%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[twocolumn]{ceurart}

@@

@@

\section{Experiments}
\section{Discussion}

>>>>

%% Options:

%% twocolumn : Two column layout.
%% hf: enable header and footer.
\documentclass[twocolumn]{ceurart}

@@

\subsection{Iterator preparation}
In order to prepare the prefix-free graph to generate the suffix array of
original pangenome we need to create several data structures.
First, we concatenate all the prefix-free segments into a single string using
a separator $\#$ and append a sentinel $\$$.
We will call this concatenation \emph{segment join}.

Next, for the segment join we calculate the suffix array and the LCP array.
For this we can use the linear time, linear space algorithms mentioned previously,
since the segment join is assumed to be much smaller than the original pangenome.

Next, we need to calculate the segment ID array.
Next, for each suffix of a segment join, we need to calculate the segment ID
and the segment position.
The segment ID tells us that the current suffix of a segment join starts with a particular segment.

@@

\section{Results}
We implemented the prefix-free graphs package in rust programming language.
There are two binary crates and one library crate included in the package.
Binary crates serve the purpose of creating prefix-free graphs from FASTA and from GFA formats.
Library crate provides an interface for working with the prefix-free graphs,
mainly an iterator of suffix array in sublinear space and linear time.

The binary crates are fasta2pfg and gfa2pfg with usage:
\begin{minted}{bash}
fasta2pfg -t triggers.txt < pangenome.fna > pfg.gfa

gfa2pfg -t triggers.txt < pangenome.gfa > pfg.gfa
\end{minted}

The library can be used from within rust programming language as follows:

\begin{minted}{rust}
let pfg = PFG::load("pfg.gfa");

for (i, sa_i) in pfg.iter().enumerate() {
    println!("{}\t{}", i, sa_i);
}
\end{minted}

\section{Discussion}
